\documentclass[12pt, a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
	 \usepackage{tabularx}

    \textheight=10in
    \pagestyle{empty}
    \raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Yash Vora}}
\end{center}


\begin{tabularx}{\textwidth}{X l}
6th Semester & 8105379361  \\
Bengaluru & vorayash97@gmail.com \\
linkedin.com/in/vorayash/ & github.com/feirydraco \\ 
\end{tabularx}

%==== Education ====%
\header{Education}
\textbf{RNS Institute of Technology}\hfill Bengaluru\\
B.E. Computer Science \textit{GPA: 8.0 (Ongoing)} \hfill 2016 - 2020\\
\vspace{2mm}
\textbf{Udacity}\hfill Remote\\
Professional Education, Computer Vision \hfill 2018 - 2018\\
\vspace{2mm}



\header{Skills}
\begin{tabular}{ l l }
	Programming Languages:         & C, C++, Java, HTML, \LaTeX                                \\
	Database:                      & MySQL, SQLite, NoSQL                                      \\
	Scripting and Version Control: & Python, Shell, Git                                        \\
	Tools:                         & Jupyter Notebooks, Eclipse, AWS Lambda, \\
 													 & AWS EC2, Amazon Alexa \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Facial Keypoint Detection}} {\sl OpenCV, PyTorch, Numpy} \\
I created a facial key point detection model. This model was then integrated into a full pipeline that takes an image, identifies any faces in the image, then detects the key points of those faces.\\
\vspace*{2mm}
{\textbf{Logic Gate Simulation w/ Conway\textquotesingle{}s Game of Life}} {\sl Python, Tkinter} \\
I created a visualisation of Conway\textquotesingle{}s Game of Life Automaton on Tkinter GUI interface. The Automaton was then used to create a non-binary automaton to create logic gates.\\
\vspace*{2mm}
{\textbf{Monopoly Master}} {\sl AWS Lambda, Alexa Skills Kit, Python} \hfill https://amzn.to/2TRYkJ4\\
A VUI based Amazon Alexa Skill developed with the intention of creating a voice-based assistant to the original Monopoly Game.\\
\vspace*{2mm}
{\textbf{Student Information System}} {\sl HTML/CSS/JS, Flask, Python} \\
An application designed to store and modify details of a particular branch of students. Resources to view data intuitively and graphically was added to make visualization easy.\\
\vspace*{2mm}



\header{Achievements}

\begin{itemize}
\item Secured 1\textsuperscript{st} place in College Project Open-House Presentation in 2nd Year. (PROP '18) 
\item Monopoly Master surpassed 1000+ unique users in US Alexa Store.
\end{itemize}

\header{Fields Of Interest}
\begin{itemize}
\item Scripting, AI, Image Proccessing, Automation, Robotics.
\end{itemize}


\header{Strengths}
\begin{itemize}
\item  Positive Attitude, Social Interaction, Hardworking, Goal Oriented.
\end{itemize}



\header{Interest and Hobbies}
\begin{itemize}
\item  Solving puzzles, mentoring.
\end{itemize}
\end{document}